%
% Math1320 - Quiz 1                                                                                                                                                                                                                                                                                                                  Math231 - Quiz 10
%

\documentclass[10pt]{article}

\usepackage{amsmath,amsthm,amsfonts,amssymb}
\usepackage[top=.5in,bottom=.5in,left=.5in,right=.75in]{geometry}
\usepackage{setspace}
\pagestyle{plain}

\setlength{\parindent}{0em}
\setlength{\parskip}{1ex}

\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\set}[1]{\{ #1 \}}
\newcommand{\vect}[1]{\mathbf{#1}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\Z}{\mathbb{Z}}

\newcommand{\ds}{\displaystyle}
\newcommand{\dx}{\hspace{2pt} dx}

\theoremstyle{definition}
\newtheorem{theorem}{Theorem}

\begin{document}

\thispagestyle{empty}

%MATH 1210 \hfill {\sc Name:} \rule{7cm}{.01cm} \\
Final Review \hfill

\vspace{.5in}
\begin{enumerate}
\setlength{\itemindent}{-5mm}

\item Find the domain of $f(x) = \frac{\sqrt{3-x}}{\ln (x+7)}.$

\item Evaluate the following limits.
\begin{enumerate}
\item $\ds \lim_{x \to -3} \frac{x^2-9}{x^2+12x+27}$
\item $\ds \lim_{x \to \infty} \frac{x^3+7x+9}{x+2}$
\end{enumerate}

\item 
\begin{enumerate}
\item What is the definition of continuity?
\item Suppose $\ds f(x) = \begin{cases} x+7 & \text{ if } x \ge 1 \\ kx - 9 & \text{ if } x<1 \end{cases}$ 

Find $k$ such that $f(x)$ is continuous. 
\end{enumerate}

\item Find the derivative of $\sqrt{x+2}$ using the limit definition of derivative.

\item
\begin{enumerate}
\item State the chain rule.
\item Suppose $h(x) = x(f \circ g(x)),$ $g(1)=2,$ $f(2)=3,$ $f'(2)=4,$ and $g'(1)=1.$ Find $h'(1).$
\end{enumerate}

\item Find $\frac{dy}{dx}$ given that $x$ and $y$ are related by $ye^x + y^2 + x^2 =7$.

\item The base of a 13 ft. ladder leaning against a wall begins to slide away from the wall. When the base is 12 ft. from the wall the base is moving at a rate of 8 ft./sec. How fast is the top of the ladder sliding down the wall?

\item 
\begin{enumerate} 
\item Sketch the graph of $f(x) = \ds \frac{x-1}{x+1}.$
\item Find the absolute extrema of $f(x)$ on $[-3,7].$ (How do you know these extrema exist? What theorem are you appealing to?)
\end{enumerate}

\item If an open box is to have a square base and a volume of 108 $in^3$ and is constructed from a tin sheet find the dimensions of the box assuming a minimum amount of material is used in its construction.

\item Solve for $x:$
\begin{enumerate}
\item $\ds \frac{1}{27^{3x+1}} = 9^x$
\item $\ds \ln (3x+e+17)= 1$
\end{enumerate}

\item Differentiate $f(x) = (x^2 + 3x+1)^{x+7}$ using logarithmic differentiation.

\item A substance has a half life of 10 days. If initially there are 110 grams of the substance find the amount present after $t$ days. How long will it take for only 20 grams of the substance to be left?

\item Find the area under $f(x) = x + \frac{1}{x} + \frac{1}{x^3}$ on $[1,3].$

\item Find a function $f(x)$ such that $f'(x) = (x+1)(x^2+7x+10)$ and $f(1)=6.$
%\newpage

\item Evaluate the following definite and indefinite integrals.
\begin{enumerate}
\item $\ds \int \frac{(\ln x)^3}{x} \dx $
\item $\ds \int _2^5 \frac{x^7+9x+6}{x^3} \dx$
\item $\ds \int \frac{e^{-1/x}}{x^{-3}} \dx$
\item $\ds \int _0^2 x^2 (x+3+7)^{5/3} \dx$
\end{enumerate}

\item When evaluating an indefinite integral why do we need to add the ``$+ \text{ } c$"?

\end{enumerate}
\end{document}


